Something with Objects and Names

### 2019-12-04 papers/ACL2020/acl2020_main.tex
add verification image to appendix

\section{ManyNames: Entry-Level Names and their Alternatives}
\label{sec:manynames}
\input{manynames}

@@

>>>>

\section{ManyNames: A Source for Entry-Level Names}
\label{sec:manynames}
\input{manynames}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{images/verification-interface.pdf}
	\caption{A screenshot of our verification task interface. Up to ten names could be shown for an image in this way (the number of available colors in the second task would increase accordingly).}
	\label{fig:verification-interface}
\end{figure*}
